\documentclass[12pt]{article}
\usepackage{import}
\input{/Users/henrytwiss/Documents/Documents/LaTeX/Vignettes/preamble.tex}

%=================%
%  Title & Index  %
%=================%
\title{Integral lattices}
\author{Henry Twiss}
\makeindex

\begin{document}
  \date{}
  \maketitle
  \section{Integral Lattices}
    Integral Lattices are ubiquitous in number theory because they provide a way to study discrete points by geometric methods. Let \(F\) be a characteristic zero field and \(V\) be an \(n\)-dimensional \(F\)-vector space with nondegenerate symmetric inner product \(\<\cdot,\cdot\>\). We say that a subset \(\L\) of \(V\) is a \textbf{integral lattice}\index{integral lattice} if \(\L\) is a free abelian group. In particular, any integral lattice \(\L\) is of the form
    \[
      \L = \Z v_{1}+\cdots+\Z v_{m},
    \]
    for some linearly independent vectors \(v_{1},\ldots,v_{m}\) of \(V\) with \(m \le n\). We say \(\L\) is \textbf{complete}\index{complete} if \(n = m\). Necessarily, \(v_{1},\ldots,v_{n}\) is a basis of \(V\). If \(e_{1},\ldots,e_{n}\) is an orthonormal basis for \(V\), write
    \[
      v_{i} = \sum_{1 \le i \le n}v_{i,j}e_{j},
    \]
    with \(v_{i,j} \in F\) for \(1 \le i,j \le n\), and define the associated \textbf{generator matrix}\index{generator matrix} \(P\) by
    \[
      P = \begin{pmatrix} v_{1,1} & \cdots & v_{n,1} \\ \vdots & & \vdots \\ v_{1,n} & \cdots & v_{n,n} \end{pmatrix}.
    \]
    Then \(P\) is the base change matrix from \(e_{1},\ldots,e_{n}\) to \(v_{1},\ldots,v_{n}\). The \textbf{covolume}\index{covolume} \(V_{\L}\) of a complete integral lattice \(\L\) is defined to be
    \[
      V_{\L} = |\det(P)|.
    \]
    By \cref{prop:base_change_quotient_determinant} and that the base change matrix between any two orthonormal basses is an orthogonal matrix and hence has determinant \(\pm 1\), the covolume is independent of the choice of bases. In particular, if \(V\) is a real or complex vector space we will take \(e_{1},\ldots,e_{n}\) to be the standard basis. We now introduce the notion of dual integral lattices. If \(\L\) is a complete integral lattice in \(V\) then the \textbf{dual}\index{dual} \(\L^{\vee}\) of \(\L\) is defined by
    \[
      \L^{\vee} = \{v \in V:\<\l,v\> \in \Z \text{ for all } \l \in \L\}.
    \]
    In other words, \(\L^{\vee}\) consists of all of the vectors in \(V\) whose inner product with elements of \(\L\) are integers. The dual integral lattice is indeed a complete integral lattice as the following proposition shows:

    \begin{proposition}\label{prop:dual_integral lattice_exists}
      If \(v_{1},\ldots,v_{n}\) is a basis for the complete integral lattice \(\L\) then the dual basis \(v_{1}^{\vee},\ldots,v_{n}^{\vee}\) is a basis for \(\L^{\vee}\). In particular, \(\L^{\vee}\) is a complete integral lattice.
    \end{proposition}
    \begin{proof}
      Let \(v \in V\) and write
      \[
        v = \sum_{1 \le j \le n}a_{i}v_{j}^{\vee},
      \]
      with \(v_{j}^{\vee} \in \R\) for all \(j\). Since \(\<v_{i},v_{j}^{\vee}\> = \d_{i,j}\) for \(1 \le i,j \le n\), it follows that \(v \in \L^{\vee}\) if and only if \(v_{j}^{\vee} \in \Z\) for all \(j\). This means that \(v_{1}^{\vee},\ldots,v_{n}^{\vee}\) is a free abelian group of rank \(n\). Hence \(\L^{\vee}\) is a complete integral lattice.
    \end{proof}

    Since the dual of the dual basis is the original basis, \((\L^{\vee})^{\vee} = \L\). We say that \(\L\) is \textbf{self-dual}\index{self-dual} if \(\L^{\vee} = \L\). For example, the integral lattice \(\Z^{n}\) is self-dual because the standard basis is self-dual. It also turns out that the covolume of the dual integral lattice is the inverse of the volume of the original integral lattice:

    \begin{proposition}\label{prop:covolume_of_dual_is_inverse}
      Let \(\L\) be a complete integral lattice in \(V\) and let \(\L^{\vee}\) be its dual. Then
      \[
        V_{\L^{\vee}} = \frac{1}{V_{\L}}.
      \]
    \end{proposition}
    \begin{proof}
      Let \(e_{1},\ldots,e_{n}\) be the standard basis for \(V\) and let \(v_{1},\ldots,v_{n}\) be a basis for \(\L\). By \cref{prop:dual_integral lattice_exists}, \(v_{1}^{\vee},\ldots,v_{n}^{\vee}\) is a basis for \(\L^{\vee}\). If \(P\) is the associated generator matrix for \(\L\) then \(P\) is the base change matrix from \(e_{1},\ldots,e_{n}\) to \(v_{1},\ldots,v_{n}\). Hence \((P^{-1})^{t}\) is the base change matrix from \(e_{1},\ldots,e_{n}\) to \(v_{1}^{\vee},\ldots,v_{n}^{\vee}\). The claim follows by \cref{prop:base_change_quotient_determinant}.
    \end{proof}
    
    We now turn to the case when \(V\) is an \(n\)-dimensional real inner product space with inner product \(\<\cdot,\cdot\>\). We let \(d\l\) be the associated Lebesgue measure on \(V\). If \(v_{1},\ldots,v_{n}\) is a basis of \(V\) so that any \(v \in V\) has the form
    \[
      v = t_{1}v_{1}+\cdots+t_{n}v_{n},
    \]
    with \(t_{i} \in \R\) for \(1 \le i \le n\), the Lebesgue measure \(d\l\) is \(dt_{1} \cdots dt_{n}\). For any measurable subset \(X \subseteq V\), we define the \textbf{volume}\index{volume} of \(X\) by
    \[
      \Vol(X) = \int_{X}\,d\l = \int_{X}\,dt_{1} \cdots dt_{n}.
    \]
    In other words, \(\Vol(X)\) is just the measure of \(X\) with respect to \(d\l\). We use this notation so that we do not have to specify the Lebesgue measure on \(V\). Note that \(\L\) acts on \(V\) by automorphisms given by translation. That is, we have a group action
    \[
      \L \x V \to V \qquad (\l,v) \mapsto \l+v.
    \]
    Moreover, \(\L\) acts properly discontinuously on \(V\) (see \cref{append:Fundamental_Domains}). To see this, let \(v \in V\) and let \(\d_{v}\) be such that \(0 < \d_{v} < \min_{1 \le i \le n}(v-v_{i})\). Then taking \(U_{v}\) to be the ball of radius \(\d_{v}\) about \(v\), the intersection \(\l+U_{v} \cap U_{v}\) is empty unless \(\l = 0\). As \(\L\) is also discrete, it follows by \cref{prop:quotient_by_discrete_property_discontinuously} that \(V/\L\) is also connected Hausdorff (recall that \(V\) is connected Hausdorff). In particular, \(V/\L\) admits a fundamental domain
    \[
      \mc{M} = \{t_{1}v_{1}+\cdots+t_{n}v_{n} \in V:0 \le t_{i} \le 1 \text{ for } 1 \le i \le n\}.
    \]
    Indeed, since \(\L\) acts by translations, it is obvious that \(\mc{M}\) is a fundamental domain for \(V/\L\). Moreover, any translation of \(\mc{M}\) by an element of \(\L\) is also a fundamental domain. As we might expect, the covolume of \(\L\) is equal to the volume of \(\mc{M}\):

    \begin{proposition}\label{prop:covolume_equals_volume_of_fundamental_domain}
      Let \(\L\) be a complete integral lattice in a finite dimensional real inner product space \(V\) and let \(\mc{M}\) be a fundamental domain for \(\L\). Then
      \[
        V_{\L} = \Vol(\mc{M}).
      \]
    \end{proposition}
    \begin{proof}
      Let \(n\) be the dimension of \(V\), \(e_{1},\ldots,e_{n}\) be an orthonormal basis of \(V\), and \(v_{1},\ldots,v_{n}\) be a basis for \(\L\). The change of variables
      \[
        x_{1}e_{1}+\cdots+x_{n}e_{n} \mapsto x_{1}v_{1}+\cdots+x_{n}v_{n},
      \]
      has the generator matrix \(P\) for \(v_{1},\ldots,v_{n}\) as its Jacobian matrix since \(P\) is the base change matrix from \(e_{1},\ldots,e_{n}\) to \(v_{1},\ldots,v_{n}\). Then
      \[
        \Vol(\mc{M}) = \int_{\mc{M}}\,d\mathbf{x} = |\det(P)|\int_{[0,1]^{n}}\,d\mathbf{x} = |\det(P)| = V_{\L},
      \]
      where the last equality follows by \cref{prop:base_change_quotient_determinant}.
    \end{proof}

    From \cref{prop:covolume_equals_volume_of_fundamental_domain} we see that the covolume of a complete integral lattice in a real inner product space is a measure of the density of the integral lattice. The smaller the covolume the smaller the fundamental domain and the more dense the integral lattice is. It turns out that for \(V\), being a integral lattice is equivalent to being a discrete subgroup:

    \begin{proposition}\label{prop:integral lattice_if_and_only_if_discrete_subgroup}
      Let \(\L\) be a subset of a finite dimensional real inner product space \(V\). Then \(\L\) is a integral lattice if and only if it is a discrete subgroup.
    \end{proposition}
    \begin{proof}
      It is clear that if \(\L\) is a integral lattice then it is a discrete subgroup. So suppose \(\L\) is a discrete subgroup. Then \(\L\) is closed (since \(V\) is a metric space). Let \(V'\) be the subspace spanned by \(\L\) and let its dimension be \(m\). Choosing a basis \(v'_{1},\ldots,v'_{m}\) of \(V'\), set
      \[
        \L' = \Z v'_{1}+\cdots+\Z v'_{m}.
      \]
      Then \(\L'\) is a complete integral lattice in \(V'\) and \(\L' \subseteq \L \subset V\). We claim that \(\L/\L'\) is finite. To see this, let \(\l\) be a representative of a coset in \(\L/\L'\) and let \(\mc{M}'\) be a fundamental domain for \(\L'\) in \(V'\). As \(\mc{M}'\) is a fundamental domain, there exists unique \(w' \in \mc{M}'\) and \(\l' \in \L'\) such that \(\l = w'+\l'\). But then \(w' = \l-\l' \in \mc{M}' \cap \L\) and since \(\mc{M}' \cap \L\) is closed, discrete, and compact, it must be finite (as \(\mc{M}'\) is compact and \(\L\) is closed and discrete). Hence there are finitely many \(w'\) and thus finitely many cosets in \(\L/\L'\). Letting \(|\L/\L'| = q\), we have \(q\L \subseteq \L'\) and therefore
      \[
        \L \subseteq \L' = \Z\frac{1}{q}v'_{1}+\cdots+\Z\frac{1}{q}v'_{m}.
      \]
      In particular, \(\L\) is a subgroup of a free abelian group and therefore is free abelian. This means \(\L\) is a integral lattice.
    \end{proof}

    As for complete integral lattices in \(V\), they are equivalent to the existence of a bounded set whose translates cover \(V\):

    \begin{proposition}\label{prop:complete_integral lattice_if_and_only_if_bounded_translates_cover}
      Let \(\L\) be a integral lattice in a finite dimensional real inner product space \(V\). Then \(\L\) complete if and only if there exists a bounded subset \(M\) of \(V\) whose translates by \(\L\) cover \(V\).
    \end{proposition}
    \begin{proof}
      First suppose \(\L\) is complete. Then we may take \(M = \mc{M}\) to be the fundamental domain of \(\L\) which is bounded and whose translates by \(\L\) cover \(V\). Now suppose \(\L\) is a integral lattice and there exists a bounded subset \(M\) of \(V\) whose translates by \(\L\) cover \(V\). Let \(W\) be the subspace of \(V\) spanned by \(\L\). Then \(W\) is closed. Moreover, \(\L\) is complete if and only if \(V = W\) and this is what we will show. So let \(v \in V\). Since the translates of \(M\) by \(\L\) cover \(V\), for every \(n \ge 1\) we may write
      \[
        nv = w_{n}+\l_{n},
      \]
      with \(v_{n} \in M\) and \(\l_{n} \in L \subset W\). As \(M\) is bounded, \(\lim_{n \to \infty}\frac{1}{n}v_{n} = 0\). Moreover, \(\frac{1}{n}\l_{n} \in W\) for every \(n\) and since \(W\) is closed we must have that \(\lim_{n \to \infty}\frac{1}{n}\l_{n}\) exists. These facts, and that \(v\) is independent of \(n\), together imply
      \[
        v = \lim_{n \to \infty}\frac{1}{n}w_{n}+\lim_{n \to \infty}\frac{1}{n}\l_{n} = \lim_{n \to \infty}\frac{1}{n}\l_{n},
      \]
      is an element of \(W\). Since \(v\) was arbitrary, \(V = W\) and hence \(\L\) is complete.
    \end{proof}

    The most important result we will require about integral lattices is \textbf{Minkowski's lattice point theorem}\index{Minkowski's lattice point theorem} which states that, under some mild conditions, a set of sufficiently large volume in \(V\) contains a nonzero point of a complete integral lattice:

    \begin{theorem*}[Minkowski's lattice point theorem]
      Let \(\L\) be a integral lattice in an \(n\)-dimensional real inner product space \(V\). Suppose \(X \subset V\) is a compact convex symmetric set. If
      \[
        \Vol(X) \ge 2^{n}V_{\L},
      \]
      then there exists a nonzero \(\l \in L\) with \(\l \in X\) 
    \end{theorem*}
    \begin{proof}
      We will prove the claim depending on if the inequality is strict or not. First suppose \(\Vol(X) > 2^{n}V_{\L}\). Consider the linear map
      \[
        \phi:\frac{1}{2}X \to V/\L \qquad \frac{1}{2}x \mapsto \frac{1}{2}x+\L.
      \]
      If \(\phi\) were injective then we would have
      \[
        \Vol\left(\frac{1}{2}X\right) = \frac{1}{2^{n}}\Vol(X) \le V_{\L}, 
      \]
      so that \(\Vol(X) \le  2^{n}V_{\L}\). This is a contradiction, so \(\phi\) cannot be injective. Hence there exists distinct \(x_{1},x_{2} \in \frac{1}{2}X\) such that \(\phi(x_{1}) = \phi(x_{2})\). Thus \(2x_{1},2x_{2} \in X\). In particular, since \(X\) is symmetric we must have \(-2x_{2} \in X\). But then the fact \(X\) is convex implies that
      \[
        \left(1-\frac{1}{2}\right)2x_{1}+\frac{1}{2}(-2x_{2}) = x_{1}-x_{2},
      \]
      is an element of \(X\). Note that \(x_{1}-x_{2} \in \L\) because \(\phi(x_{1}) = \phi(x_{2})\) and \(\phi\) is linear. Then \(\l = x_{1}-x_{2}\) is a nonzero element of \(\L\) with \(\l \in X\). Now suppose \(\Vol(X) = 2^{n}V_{\L}\). Then
      \[
        \Vol((1+\e)X) = (1+\e)^{n}\Vol(X) = (1+\e)^{n}2^{n}V_{\L} > 2^{n}V_{\L}.
      \]
      What we have just proved shows that there exists a nonzero \(\l_{\e} \in \L\) with \(\l_{\e} \in (1+\e)X\). In particular, if \(\e \le 1\) then \(\l_{\e} \in 2X \cap \L\). The set \(2X \cap \L\) is compact and discrete, because \(X\) is compact and \(\L\) is discrete, and therefore is finite. But as this holds for all \(\e \le 1\), the sequence \((\l_{\frac{1}{n}})_{n \ge 1}\) belongs to the finite set \(2X \cap \L\) and so must converge to a point \(\l\). Since \(\L\) is discrete and the \(\l_{\frac{1}{n}}\) are nonzero so too is \(\l\). As \(\l\) is an element of
      \[
        \bigcap_{n \ge 1}\left(1+\frac{1}{n}\right)X,
      \]
      and \(X\) is closed, \(\l \in X\) as well. Thus we have found a nonzero \(\l \in L\) with \(\l \in X\) and we are done.
    \end{proof}
\end{document}